### 2017-03-03 Conclusion/Conclusion.tex
Own final read through

As more data are collected during the remainder of Run 2, and in the 
future, searches for \ac{MSSM} Higgs bosons in the di-tau final
state will continue. If no such Higgs bosons are found, these searches
will be able to exclude even more of the \mA-\tanb~plane in specific
\ac{MSSM} benchmark scenarios, although not all of the \mA-\tanb~plane
will become accessible. A projection of the results of the 2015 \ac{MSSM}
analysis to integrated luminosities of $300\,\invfb$ and $3000\,\invfb$ \cite{HTT-projection} is
shown in figure \ref{fig:mssm_projection_fig}. Even with an integrated luminosity of
$3000\,\invfb$ it is not possible to exclude the full \mA-\tanb~plane of this scenario,
as the branching ratio of $\PHiggsps/\PHiggs$ into di-tau pairs 
is very low in the high-\mA and low-tanb~corner. This region can be accessed 
via searches for the $\PHiggsps/\PHiggs \rightarrow \Ptop\APtop$ decay, which
has an enhanced branching ratio in this region. To fully cover this
parameter space it will therefore start to become more and more
important to combine searches for heavy Higgs bosons in different final states.
Doing this will give the best sensitivity to possible
heavy Higgs bosons, or in the absence of these particles exclusion
of the scenarios that predict them.

>>>>

As more data are collected during the remainder of Run 2, and in the 
future, searches for \ac{MSSM} Higgs bosons in the di-tau final
state will continue. If no such Higgs bosons are found, these searches
will be able to exclude even more of the \mA-\tanb~plane in specific
\ac{MSSM} benchmark scenarios, although not all of the \mA-\tanb~plane
will become accessible. A projection of the results of the 2015 \ac{MSSM}
analysis to integrated luminosities of $300\,\invfb$ and $3000\,\invfb$ \cite{HTT-projection} is
shown in figure \ref{fig:mssm_projection_fig}. Even with an integrated luminosity of
$3000\,\invfb$ it is not possible to exclude the full \mA-\tanb~plane of this scenario,
as the branching ratio of $\PHiggsps/\PHiggs$ into di-tau pairs 
is very low in the high-\mA~and low-tanb~corner. This region can be accessed 
via searches for the $\PHiggsps/\PHiggs \rightarrow \Ptop\APtop$ decay, which
has an enhanced branching ratio in this region. To fully cover this
parameter space it will therefore start to become more and more
important to combine searches for heavy Higgs bosons in different final states.
Doing this will give the best sensitivity to possible
heavy Higgs bosons, or in the absence of these particles exclusion
of the scenarios that predict them.

### 2017-03-03 Detector/Detector.tex
Own final read through

The \acf{LHC} \cite{lhc-machine}  is a $26.7\,\kilo\metre$ long synchrotron hadron accelerator and collider below the surface of the 
Franco-Swiss border near Geneva. It
is installed in the tunnel that previously hosted the Large Electron Positron accelerator \cite{lep-design}
that was operated by \acf{CERN} between 1989 and 2000.

@@

The data-taking efficiency of CMS is not 100\%, as parts of the detector might be
switched off while collisions are ongoing. In 2012 the data-taking 
efficiency was 93.5\%, in 2015 it was 90.3\% and in 2016 it was 92.0\%
From all of the data that is recorded only a subset is used for analysis. Data is 
certified as good for use in analyses if it is known that all relevant sub-detectors
were functioning correctly. In 2012 the certification efficiency was 90.4\%, 
meaning all sub-detectors were working well for a dataset corresponding to $19.7\,\invfb$. %MAYBE COME BACK TO LATER?
Due to cryogenic issues the certification efficiency with the magnet operating
at $3.8\,\tesla$ was 60.4\% in 2015, leading to $2.3\,\invfb$ of 
analysable data for which the full detector was operational. An additional $0.6\,\invfb$
was taken with the \ac{CMS} magnet switched off. For the full 2016 p-p running period
the certification efficiency was 95.0\%, resulting in $35.9\,\invfb$ of data marked good %FIXME: certification efficiency
for use in analyses.

@@

For the measurement of physical quantities \ac{CMS} uses a coordinate
system with the origin centred at the nominal collision point
inside the experiment. The $y$ axis points vertically upward, the $x$ axis
points radially inward toward the centre of the \ac{LHC} ring. The $z$ axis
points along the beam direction. As such the transverse momentum and energy, 
\pT~and \ET, are defined by the $x$- and $y$-components of the momentum and energy.
The azimuthal angle $\phi$ is measured in the $x$-$y$ plane with respect to the $x$ axis  
and the polar angle $\theta$ is measured with respect to the $z$ axis. A coordinate
more frequently used than the polar angle is the pseudorapidity $\eta = -\ln{[\tan{\frac{\theta}{2}}]}$.%Look up: differences in eta are lorentz-invariant
Distances in the $\eta$-$\phi$ plane are given as $\Delta R = \sqrt{(\Delta\eta)^2+(\Delta\phi)^2}$.

@@

Around the pixel detector the tracking system is made up of a silicon
strip detector divided into four sub-systems. The first part of the
silicon strip tracker consists of the \ac{TIB} and \ac{TID}, providing four layers of
silicon strip detectors in the barrel plus three disks at both ends. These two systems
extend out up to a radius of $55\,\cm$. The barrel layers and disks each consist
of silicon strips which are $10\,\cm$ long, $80$--$141\,\micron$ wide and $320\,\micron$ thick. The \ac{TIB} and \ac{TID}
provide four measurements of the $r$-$\phi$ position with a resolution of $23$--$35\,\micron$. 
The \ac{TIB} and \ac{TID} are surrounded by the \ac{TOB}, which consists of six layers of silicon strip sensors extending
up to an outer radius of $116\,\cm$ and up to $z=\pm\,118\,\cm$. The strips in the \ac{TOB} are $500\,\micron$ thick, 
around $25\,\cm$ long and $122$--$183\,\micron$ 
wide providing 6 measurements of $r$ and $\phi$, with a resolution
of $35$--$53\,\micron$. Beyond the $z$ range covered by the \ac{TOB}, coverage is provided by the \ac{TEC},
consisting of nine disks of strips. In the \ac{TEC} the strip thickness ranges from $320$--$500\,\micron$ and 
the the strip width ranges from $97$--$184\,\micron$. %FIXME: look up why
This part of the system provides up to nine $\phi$ measurements.

Some of the strip modules in the detector carry a second strip detector module mounted back-to-back with a stereo angle %FIXME WTF?
of $100\,$mrad, in order to provide measurements of the $z$ coordinate in the barrel. This is achieved with a resolution of $230$--$530\,\micron$.

@@

\subsection{Electromagnetic calorimeter}
\label{sec:CMSLHC_CMS_ecal}
The \ac{ECAL} \cite{cms-jinst} is a hermetic homogeneous calorimeter
made of nearly $76\,000$ lead tungstate (PbWO$_4$) crystals. It has very
good energy resolution, is highly granular and has a fast response, all qualities 
which are needed to be able to detect $\PHiggslight\rightarrow \Pphoton\Pphoton$ decays.

@@

To preserve the energy resolution the crystals and
photodetectors need to be kept stable within $18\pm 0.05^{\circ}$C
as the number of scintillation photons emitted by the crystals,
and the amplification of the photodetectors, are temperature dependent.
This nominal operating temperature, is ensured by 
supplying the detector with water at the same temperature.

@@

In the barrel the \ac{HCAL}
has a thickness of between 5.82 and 10.6 interaction lengths, which is not 
sufficient to identify, for example, late-starting showers. The \ac{HO}, sitting
outside of the magnet and using the coil as an additional absorber, extends the 
thickness to at least 11.8 interaction lengths. 
As in the \ac{HB} the active material of the \ac{HO} consists of plastic scintillator tiles which roughly
map on the granularity of the tiles in the \ac{HB}, and are read out via the same mechanism. %by feeding the light
%to a hybrid photodiode via wavelength-shifting fibres.
%WTF: wavelength-shifting fibres

@@

\subsection{Muon system}
\label{sec:CMSLHC_CMS_muons}
Accurate muon identification is one of the requirements of the \ac{CMS} 
experiment. High muon identification efficiency and precise muon momentum 
resolution are key to the success of the experiment, as muons are
very important for the detection of $\PHiggslight\rightarrow \PZ\PZ \rightarrow 4\ell$ decays. In addition to that,
muons appear in the final states of many of the \ac{BSM} signatures the experiment is searching for.

@@

In the endcaps, where both the muon rate and the radiation levels are higher, the \acp{CSC} provide
measurements of the muon track. These detectors are radiation hard,
and have a fast response and fine segmentation.
Each of the \ac{CSC} modules is a wedge-shaped
multi-wire proportional chamber %WTF
with six gaseous chambers bounded by cathode plates. Sensitive
strips are placed on these plates in the 
radial direction, to measure the muon coordinate in the  $r$--$\phi$ plane.
Anode wires between the cathode planes
run along the $\phi$ direction and provide a measurement of
$\eta$. The resolution of the $r$--$\phi$ measurement is $40$--$120\,\micron$ \cite{cms-muon-7tev}.

@@

To obtain precise muon momentum resolution information from 
the tracker hits has to be combined with measurements in the
muon stations. The momentum resolution of the muon system
alone is 9\% for muons with \pT~up to $200\,\GeV$, and varies with $\eta$ 
between $15$--$40\%$ for muons with \pT~of $1\,\TeV$ \cite{cms-jinst}. %ADD FORMULA

@@

The trigger system consists of two stages: the \ac{L1} trigger and the \ac{HLT}. which only makes use of
The \ac{L1} trigger only makes use of front-end electronics and reduces the event rate 
from $40\,$MHz to around $100\,$kHz. The \ac{HLT} 
runs on a computer farm with around $13\,000$ CPU cores \cite{cms-trigger}.
During \ac{LS1} and the year-end technical stop at the end of 2015 the \ac{L1} trigger was
replaced by a completely upgraded system \cite{cms-trigger-tdr}, which provides, amongst other 
things, improved object isolation, hadronic tau identification, muon \pT~resolution and
jet finding with respect to the system used during Run 1.
An overview of the data flow in the \ac{L1} trigger is given in figure \ref{fig:CMS_Trigger}.

>>>>

The \acf{LHC} \cite{lhc-machine}  is a $26.7\,\kilo\metre$ long synchrotron hadron accelerator and collider below the surface of the 
Franco-Swiss border near Geneva. It
is installed in the tunnel that previously hosted the \acf{LEP} accelerator \cite{lep-design}
that was operated by \acf{CERN} between 1989 and 2000.

@@

The data-taking efficiency of CMS is not 100\%, as parts of the detector might be
switched off while collisions are ongoing. In 2012 the data-taking 
efficiency was 93.5\%, in 2015 it was 90.3\% and in 2016 it was 92.0\%.
From all of the data that is recorded only a subset is used for analysis. Data is 
certified as good for use in analyses if it is known that all relevant sub-detectors
were functioning correctly. In 2012 the certification efficiency was 90.4\%, 
meaning all sub-detectors were working well for a dataset corresponding to $19.7\,\invfb$. %MAYBE COME BACK TO LATER?
Due to cryogenic issues the certification efficiency with the magnet operating
at $3.8\,\tesla$ was 60.4\% in 2015, leading to $2.3\,\invfb$ of 
analysable data for which the full detector was operational. An additional $0.6\,\invfb$
was taken with the \ac{CMS} magnet switched off. For the full 2016 p-p running period
the certification efficiency was 95.0\%, resulting in $35.9\,\invfb$ of data marked good %FIXME: certification efficiency
for use in analyses.

@@

For the measurement of physical quantities \ac{CMS} uses a coordinate
system with the origin centred at the nominal collision point
inside the experiment. The $y$ axis points vertically upward, the $x$ axis
points radially inward toward the centre of the \ac{LHC} ring. The \mbox{$z$ axis}
points along the beam direction. As such the transverse momentum and energy, 
\pT~and \ET, are defined by the $x$- and $y$-components of the momentum and energy.
The azimuthal angle $\phi$ is measured in the $x$-$y$ plane with respect to the $x$ axis  
and the polar angle $\theta$ is measured with respect to the $z$ axis. A coordinate
more frequently used than the polar angle is the pseudorapidity $\eta = -\ln{[\tan{\frac{\theta}{2}}]}$. %Look up: differences in eta are lorentz-invariant
Distances in the $\eta$-$\phi$ plane are given as $\Delta R = \sqrt{(\Delta\eta)^2+(\Delta\phi)^2}$.

@@

Around the pixel detector the tracking system is made up of a silicon
strip detector divided into four sub-systems. The first part of the
silicon strip tracker consists of the \ac{TIB} and \ac{TID}, providing four layers of
silicon strip detectors in the barrel plus three disks at both ends. These two systems
extend out up to a radius of $55\,\cm$. The barrel layers and disks each consist
of silicon strips which are $10\,\cm$ long, $80$--$141\,\micron$ wide and $320\,\micron$ thick. The \ac{TIB} and \ac{TID}
provide four measurements of the $r$-$\phi$ position with a resolution of $23$--$35\,\micron$. 
The \ac{TIB} and \ac{TID} are surrounded by the \ac{TOB}, which consists of six layers of silicon strip sensors extending
up to an outer radius of $116\,\cm$ and up to $z=\pm\,118\,\cm$. The strips in the \ac{TOB} are $500\,\micron$ thick, 
around $25\,\cm$ long and $122$--$183\,\micron$ 
wide providing six measurements of $r$ and $\phi$, with a resolution
of $35$--$53\,\micron$. Beyond the $z$ range covered by the \ac{TOB}, coverage is provided by the \ac{TEC},
consisting of nine disks of strips. In the \ac{TEC} the strip thickness ranges from $320$--$500\,\micron$ and 
the the strip width ranges from $97$--$184\,\micron$. %FIXME: look up why
This part of the system provides up to nine $\phi$ measurements.

Some of the strip modules in the detector carry a second strip detector module mounted back-to-back with a stereo angle %FIXME WTF?
of $100\,$mrad, in order to provide measurements of the \mbox{$z$ coordinate} in the barrel. This is achieved with a resolution of $230$--$530\,\micron$.

@@

\subsection{Electromagnetic calorimeter}
\label{sec:CMSLHC_CMS_ecal}
The \ac{ECAL} \cite{cms-jinst} is a hermetic homogeneous calorimeter
made of nearly $76\,000$ lead tungstate (PbWO$_4$) crystals. It has very
good energy resolution, is highly granular and has a fast response, all qualities 
which are needed to be able to detect $\PHiggs\rightarrow \Pphoton\Pphoton$ decays.

@@

To preserve the energy resolution the crystals and
photodetectors need to be kept stable within $18\pm 0.05^{\circ}$C
as the number of scintillation photons emitted by the crystals,
and the amplification of the photodetectors, are temperature dependent.
This nominal operating temperature is ensured by 
supplying the detector with water at the same temperature.

@@

In the barrel the \ac{HCAL}
has a thickness of between 5.82 and 10.6 interaction lengths, which is not 
sufficient to identify, for example, late-starting showers. The \ac{HO}, sitting
outside of the magnet and using the coil as an additional absorber, extends the 
thickness to at least 11.8 interaction lengths. 
As in the \ac{HB} the active material of the \ac{HO} consists of plastic scintillator tiles which roughly
map the granularity of the tiles in the \ac{HB}, and are read out via the same mechanism. %by feeding the light
%to a hybrid photodiode via wavelength-shifting fibres.
%WTF: wavelength-shifting fibres

@@

\subsection{Muon system}
\label{sec:CMSLHC_CMS_muons}
Accurate muon identification is one of the requirements of the \ac{CMS} 
experiment. High muon identification efficiency and precise muon momentum 
resolution are key to the success of the experiment, as muons are
very important for the detection of $\PHiggs\rightarrow \PZ\PZ \rightarrow 4\ell$ decays. In addition to that,
muons appear in the final states of many of the \ac{BSM} signatures the experiment is searching for.

@@

In the endcaps, where both the muon rate and the radiation levels are higher, the \acp{CSC} provide
measurements of the muon track. These detectors are radiation hard,
and have a fast response and fine segmentation.
Each of the \ac{CSC} modules is a wedge-shaped
multi-wire proportional chamber %WTF
with six gaseous chambers bounded by cathode plates. Sensitive
strips are placed on these plates in the 
radial direction, to measure the muon coordinate in the  $r$--$\phi$ plane.
Anode wires between the cathode planes
run along the \mbox{$\phi$ direction} and provide a measurement of
$\eta$. The resolution of the $r$--$\phi$ measurement is $40$--$120\,\micron$ \cite{cms-muon-7tev}.

@@

To obtain precise muon momentum resolution, information from 
the tracker hits has to be combined with measurements in the
muon stations. The momentum resolution of the muon system
alone is 9\% for muons with \pT~up to $200\,\GeV$, and varies with $\eta$ 
between $15$--$40\%$ for muons with \pT~of $1\,\TeV$ \cite{cms-jinst}. %ADD FORMULA

@@

The trigger system consists of two stages: the \ac{L1} trigger and the \ac{HLT}. 
The \ac{L1} trigger only makes use of front-end electronics and reduces the event rate 
from $40\,$MHz to around $100\,$kHz. The \ac{HLT} 
runs on a computer farm with around $13\,000$ CPU cores \cite{cms-trigger}.
During \ac{LS1} and the year-end technical stop at the end of 2015 the \ac{L1} trigger was
replaced by a completely upgraded system \cite{cms-trigger-tdr}, which provides, amongst other 
things, improved object isolation, hadronic tau identification, muon \pT~resolution and
jet finding with respect to the system used during Run 1.
An overview of the data flow in the \ac{L1} trigger is given in figure \ref{fig:CMS_Trigger}.
